%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{verbatim}
\usepackage{xcolor}
\ifdefined\pdfglyphtounicode
\input{glyphtounicode}
\fi
\usepackage{hyperref}



%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\ifdefined\pdfgentounicode
\pdfgentounicode=1
\fi

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Wonjun Jo} \\ \vspace{1mm}
    {\small
    \href{mailto:jo1jun@postech.ac.kr}{jo1jun@postech.ac.kr} \\ %$|$
    \href{https://jo1jun.github.io/}{\underline{Website}} $|$
    \href{https://scholar.google.com/citations?user=-WfW-fUAAAAJ&hl=ko}{\underline{Scholar}} $|$
    \href{https://github.com/jo1jun}{\underline{Github}} $|$
    \href{https://www.linkedin.com/in/wonjun-jo-a21582300/}{\underline{LinkedIn}}
    }
\end{center}

%-----------RESEARCH INTERESTS-----------
\section{Research Interests}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \item{\textbf{Self-Supervised and Multi-Modal Learning for World Models in Embodied AI:}}\vspace{-1.5mm}
    \small{\item{Preserving and improving World Model generalization through self-supervised and multi-modal learning toward robust Embodied AI, with recent focus on VLA/WAM for robotics and sound/tactile signals for holistic world understanding.}}
 \end{itemize}
 
%-----------PUBLICATIONS-----------
\newcommand{\refnumbering}[1]{\noindent[\arabic{#1}]\stepcounter{#1}~}
\newcommand{\publicationSummary}[1]{\vspace{0.5mm}\begin{itemize}[leftmargin=0.34in, topsep=2pt, itemsep=0pt, parsep=0pt]\item \small{#1}\end{itemize}\vspace{0.5mm}}
\newcounter{cntinter}\stepcounter{cntinter}
\newcounter{cntdom}\stepcounter{cntdom}
\section{Publications}

\refnumbering{cntinter}\,
{\textbf{\underline{Wonjun Jo}}, Nam Hyeon-Woo, Yohan Park, Hyunwoo Ha, Tae-Hyun Oh,
``When Fine-Tuning Drifts: Mitigating Policy Drift with Base Action-Field Regularization,''}
{\textcolor{gray}{\textit{Under-review}}}.	
\publicationSummary{Mitigating policy drift for robust few-shot fine-tuning of pretrained robot policies.}
    \vspace{2mm}

\refnumbering{cntinter}\,
{\textbf{\underline{Wonjun Jo}}, Hyunwoo Ha, Kim Ji-Yeon, Hawook Jeong, Tae-Hyun Oh,
``LiDAR-Anchored Collaborative Distillation for Robust 2D Representations,''}
{\textit{IEEE Robotics and Automation Letters (RA-L)}, 2026}.
\publicationSummary{Improving the robustness and generalization of self-supervised visual representations with LiDAR guidance.}
    \vspace{2mm}

\refnumbering{cntinter}\,
{Yohan Park, Hyunwoo Ha, \textbf{\underline{Wonjun Jo}}, Tae-Hyun Oh,
``DarkQA: Benchmarking Vision-Language Models on Visual-Primitive Question Answering in Low-Light Indoor Scenes,''}
{\textit{IEEE Robotics and Automation Letters (RA-L)}, 2026}.
\publicationSummary{Benchmarking the robustness of embodied vision-language models under low-light conditions.}
    \vspace{2mm}

\refnumbering{cntinter}\,
{\textbf{\underline{Wonjun Jo}}, Hyunwoo Ha, Kim Ji-Yeon, Hawook Jeong, Tae-Hyun Oh,
``Self-Supervised Collaborative Distillation: Enhancing Lighting Robustness and 3D Awareness,''}
{Workshop on Wild3D, \textit{IEEE/CVF International Conference on Computer Vision (ICCV)}, 2025}.
\publicationSummary{Improving pretrained visual representations for lighting robustness and 3D-aware generalization.}
    \vspace{2mm}

\refnumbering{cntinter}\,
{\textbf{\underline{Wonjun Jo}}, Kwon Byung-Ki, Kim Ji-Yeon, Hawook Jeong, Kyungdon Joo, Tae-Hyun Oh,
``The Devil is in the Details: Simple Remedies for Image-to-LiDAR Representation Learning,''}
{\textit{Asian Conference on Computer Vision (ACCV)}, 2024}.
\publicationSummary{Improving self-supervised image-to-LiDAR representation learning for robust 3D perception.}
    \vspace{2mm}


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
    \resumeProjectHeading
          {\textbf{Self-Supervised Learning Method Utilizing Camera-LiDAR Correlation} \\ \textbf{for Autonomous Driving}}{Jan. 2023 -- Dec. 2024}
          \resumeItemListStart
            \resumeItem{Proposed a novel self-supervised learning method for improving 2D representation using LiDAR.}
            \resumeItem{Proposed remedies for improving self-supervised image-to-LiDAR distillation method.}
            \resumeItem{Funded by the RideFlux Inc., South Korea.}
    \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Deformable Object Recognition Technology Research}}{Mar. 2022 -- Dec. 2022}
          \resumeItemListStart
            \resumeItem{Developed deformable object recognition algorithm on multi-spectral images.}
            \resumeItem{Developed motion vector estimation algorithm for deformable objects using LiDAR.}
            \resumeItem{Funded by the Agency for Defense Development (ADD), South Korea.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------PATENTS-----------
\section{Patents}
    \resumeSubHeadingListStart
      \resumeProjectHeading
    {\textbf{Self-Supervised Learning Method, Computing Device, and Computer Program} \\ \textbf{Using Synchronized Sensor Data and Unsynchronized Sensor Data}}{2023}
    \resumeItemListStart
      \resumeItem{Republic of Korea. 10-2023-0146900}
    \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------Academic Services-----------
\section{Academic Services}
    \resumeSubHeadingListStart
        \resumeProjectHeading
        {\textbf{Journal Reviewer}}{}
          \resumeItemListStart
            \resumeItem{The Visual Computer: International Journal of Computer Graphics (TVCJ), 2023}
          \resumeItemListEnd
        \resumeProjectHeading
        {\textbf{Conference Reviewer}}{}
          \resumeItemListStart
            \resumeItem{Conference on Robot Learning (CoRL), 2026}
            \resumeItem{International Conference on Robotics and Automation (ICRA), 2023}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
      \resumeSubheading
      {POSTECH}{Pohang, South Korea}
      {Joint M.S \& Ph.D. in Electrical Engineering (Advisor: Tae-Hyun Oh)}{Mar. 2022 -- \ \ \ \ \ \ \ \ \ \ \ \ \ }
    \resumeSubheading
      {Inha University}{Incheon, South Korea}
      {B.S. in Computer Engineering}{Mar. 2018 -- Feb. 2022}
  \resumeSubHeadingListEnd

%-----------Experience-----------
\section{Experience}
  \resumeSubHeadingListStart    
    \resumeSubheading
      {KIST Physical AI Research Scientist Internship}{Seoul, South Korea}
      {Korea Institute of Science and Technology (Advisor: \href{https://scholar.google.com/citations?user=XA8EOlEAAAAJ\&hl=en}{In So Kweon})}{Jul.~2026 -- Present}
      \resumeItemListStart
        \resumeItem{World models for physical robot AI agents.}
      \resumeItemListEnd
    \resumeSubheading
      {POSTECH Student Internship}{Pohang, South Korea}
      {Pohang University of Science and Technology (Advisor: \href{https://ami.kaist.ac.kr/members/tae-hyun-oh}{Tae-Hyun Oh})}{Jun.~2021 -- Aug.~2021}
      \resumeItemListStart
        \resumeItem{Knowledge distillation for human mesh reconstruction.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
              
%-----------EXTRA SECTION-----------
\section{Extra}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Deep Learning Seminar}}{}
          \resumeItemListStart
            \resumeItem{POSTECH AMILab seminar \href{https://www.youtube.com/channel/UCAwBiEllpMRNGyGQ2hRVCIg}{[YouTube]}}
            \resumeItem{POSTECH EE-group deep learning seminar}
            \resumeItem{Attending POSTECH PAIR (CVLab, CGLab, MLLab, AMILab) seminar}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Teaching Experiences}}{}
          \resumeItemListStart
            \resumeItem{[EECE454] Introduction to Machine Learning, POSTECH}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
